### 2009-07-06 doc/tech_doc/sec/SecurityFrameworkofARC1.tex
move sec doc into tech_doc directory

% This file was converted to LaTeX by Writer2LaTeX ver. 0.9.3

@@

\documentclass[a4paper]{article}

@@

\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}

@@

\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=Aleksandr Konstantinov, pdfsubject=, pdfkeywords=}

@@

\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\arabic{subsection}}
\renewcommand\thesubsubsection{\arabic{subsection}.\arabic{subsubsection}}
\renewcommand\theparagraph{\arabic{subsection}.\arabic{subsubsection}.\arabic{paragraph}}

@@

\newcommand\liststyleLii{%

@@

@@

\author{Aleksandr Konstantinov}
\date{2009-01-19}

@@

\bigskip
\clearpage\clearpage\pagestyle{Convertv}

@@

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{delegtion.pdp} -- Delegation PDP}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The Delegation PDP is basically similar to Arc PDP, except it uses the
delegation policy parsed from remote proxy credential by
\textit{delegation.collector}, and evaluates the request against
delegation policy. See section \ref{bkm:Ref204009393}for the design
idea and use case of delegation policy in fine-grained identity
delegation.}

@@

{\selectlanguage{english}\itshape\color{black}
\ \ Rule (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Subjects (1)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ Subject (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ Attribute (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ Resources (0-1)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ Resource (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Actions (0-1)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ Action (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Conditions (0-1)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ Condition (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ Attribute (1-)}

@@

{\selectlanguage{english}\itshape\color{black}
\ \ RequestItem (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Subject (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ SubjectAttribute (1-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Resource (0-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Action (0-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ Context (0-)}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ ContextAttribute (1-)}

@@

{\selectlanguage{english}\upshape\color{black}
Each kind of Security Attribute is represented by own class inherited
from parent SecAttr class
{\textless}arc/message/SecAttr.h{\textgreater}. Each Security Attribute
stores it{\textquotesingle}s information in internal format and is
capable to export it to one of predefined formats using Export()
method. Currently only supported format is ARC Policy/Request XML
document described in Section \ref{bkm:Ref204009564}and
\ref{bkm:Ref204009595}}

{\selectlanguage{english}\upshape\color{black}
Collectors of Security Attributes instantiate corresponding classes and
link them to Secuirity Attributes containers - MessageAuth
{\textless}arc/message/MessageAuth.h{\textgreater} and
MessageAuthContext {\textless}arc/message/Message.h{\textgreater}
storing collected attributes per request and per session
correspondingly. Each attribute is assigned a name. Current
implementations of Security Attributes Collectors are either integrated
into existing MCCs or implemented as separate SecHandler plugins. See
Section \ref{bkm:Ref204009636}for available Collectors and
corresponding Security Attributes. }

@@

\liststyleWWviiiNumviii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Arc PDP makes use of Security Attributes containing identities of
client, resource and requested action. It evaluates either all or
selected set of attributes against specified Policy documents thus
making it possible to enforce policies defined/selected by service
providers. }
\item {\selectlanguage{english}\color{black}
Delegation PDP is described below in Section \ref{bkm:Ref204009695}}
\end{itemize}
\subsubsection[Available collectors]{Available collectors}
\label{bkm:Ref204009636}{\selectlanguage{english}\upshape\color{black}
Here Security Attribute collectors distributed as part of the ARC1 are
described except those used for Delegation Restrictions. Those are
described in Section \ref{bkm:Ref204009734}}

@@

{\selectlanguage{english}\color{black}
Each set of attributes is acompanied by identifier of service which
provided those attributes. It is made of \textit{voname} element with
name of VO followed by optional element \textit{hostname} with hostname
and port of service. Here is an example}

@@

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at SOAP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/endpoint &
\selectlanguage{english}\color{black} To element of WS-Addressing
structure\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/operation &
\selectlanguage{english}\color{black} SOAP top level element name
without namespace prefix\\\hline
\selectlanguage{english}\color{black} Context &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace &
\selectlanguage{english}\color{black} Namespace of SOAP top level
element\\\hline
\end{supertabular}
\end{flushleft}
\subsection[Delegation]{Delegation}
\label{bkm:Ref204009393}\subsubsection[Delegation
Architecture]{Delegation Architecture}
\label{bkm:Ref204009914}{\selectlanguage{english}\upshape\color{black}
In current implementation delegation is achieved through Identity
Delegation implemented using X509 Proxy Certificates as defined in RFC
3820. Client wishing to allow service to act on it{\textquotesingle}s
behalf provides Proxy Certificate to the service using Web Service
based Delegation interface described in Section \ref{bkm:Ref204009766}}

@@

{\selectlanguage{english}\upshape\color{black}
Each deployment implementing Delegation Restrictions must use dedicated
Security Handler plugin (see section \ref{bkm:Ref204009818}) to collect
all Policy documents from Proxy Certificates used for establishing
secure connection. Then those documents must be processed by dedicated
Policy Decision Point plugin (see section \ref{bkm:Ref204009855}) to
make a final decision based on collected Policies and various
information about client{\textquotesingle}s identity and requested
operation. Service or MCC chain supporting Delegation Restrictions must
accept negative decision of this PDP as final and do not override it
with any other decision based on other policies.}

\subsubsection[Delegation Collector]{Delegation Collector}
\label{bkm:Ref204009734}{\selectlanguage{english}\upshape\color{black}
This Security Attribute is collected by dedicated Security Handler
plugin named {\textquotedbl}delegation.collector{\textquotedbl}
avaialble as part of the ARC1 distribution. It extracts policy document
stored inside X509 certificate proxy extension as defined in RFC3820
and described in Section \ref{bkm:Ref204009914}All proxy certificates
in a chain provided by client are examined and all available policies
are extracted. }

@@

\subsubsection[Delegation interface]{Delegation interface}
\label{bkm:Ref204009766}{\selectlanguage{english}\upshape\color{black}
Delegation interface in the ARC1 is implemented using Web Service
approach. Each ARC1 service wishing to act on behalf of client identity
implements this interface in order to accept delegated credentials.
Here is how delegation procedure works (also shown in figures
\ref{seq:refFigure7} and \ref{seq:refFigure8}) :}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure7}}. The
flow diaram of delegation procedure with multiple second step and
session expiration. 
\par}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure8}}. The
flow diagram of delegation procedure with certificate transfered as
payload of service specific message. 
\par}

@@

{\selectlanguage{english}\upshape\color{black}
See Section \ref{bkm:Ref204009974}for the explanation of ARC Policy.}

@@

{\selectlanguage{english}\upshape\color{black}
There is an example policy for echo service below. See Section
\ref{bkm:Ref204009564}for the policy schema. The example policy is
\ made of following elements: }

@@

\subsubsection{PDP Service Invoker configuration}

@@

\subsubsection[X509Token SecHandler configuration]{X509Token SecHandler
configuration}
{\selectlanguage{english}\upshape\color{black}
Configuration XML schema with comments available at
\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}{\textstyleInternetlink{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/x509tokensh/X509TokenSH.xsd}}.}

@@

\subsection[Using Shibboleth IdP for Authentication and
Attribute{}-based Authorization]{Using
\foreignlanguage{english}{Shibboleth} IdP for Authentication and
Attribute-based Authorization}
{\selectlanguage{english}\color{black}
\ \ \ \ In grid community, GSI (grid security infrastructure) is the
de-facto standard about transport level communication for the legacy
grid solution, which implements some enhancement (such as delegation)
based on standard SSL3.0/TLS1.0. In ARC1, besides that GSI is supported
for talking with external grid services which are based on GSI, the
standard TLS/SSL is also supported.}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure
{\refstepcounter{Figure}\theFigure\label{seq:refFigure5}}.\textbf{
}SAML2.0 SSO profile in ARC
\par}

{\selectlanguage{english}\color{black}
\ The steps shows in Figure \ref{seq:refFigure5} are described as
follows:}

\liststyleLii
\begin{enumerate}
\item {\selectlanguage{english}\color{black}
The client uses the user agent interface to launch a HTTP request
including the IdP name (to which the user belongs) to the service side.
The endpoint of the SP (Service Provider) service is the same as that
of the other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that the user who would
access the target services should better know where is he from
initially.}
\item {\selectlanguage{english}\color{black}
The SP Service searches the metadata (we use the same metadata format as
defined in Shibboleth) and gets the location of the single sign-on
service (hosted in IdP) and also the location of assertion consuming
service (hosted in this SP itself) in order to compose the SAML
{\textless}samlp:AuthnRequest{\textgreater} message. Then SP Service
issues this {\textless}samlp:AuthnRequest{\textgreater} message by
using its own X.509 certificate (note that in the SAML SSO profile,
X.509 certificates are still needed for IdP and SP) and sends back to
user agent.}
\item {\selectlanguage{english}\color{black}
User agent sends the {\textless}samlp:AuthnRequest{\textgreater} message
to the Identity Provider.}
\item {\selectlanguage{english}\color{black}
Identity Provider requires an act of authentication. The authentication
mechanism is outside of the SAML2.0 SSO profile. Shibboleth IdP
implementation chooses some login handlers for authentication. The
current user agent implementation is compatible with the
Username/Password login handler of Shibboleth IdP. Through the HTTP
protocol, the user agent will feed IdP with the username/password which
has been given by the caller of user agent interface.}
\item {\selectlanguage{english}\color{black}
Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquoteright}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider.}
\item {\selectlanguage{english}\color{black}
The SP Service verifies and checks the SAML response, decrypts and
stores the SAML assertion into session/connection context. The SAML
assertion includes the {\textless}saml:AuthnStatement{\textgreater} and
{\textless}saml:AttributeStatement{\textgreater}.}
\item {\selectlanguage{english}\color{black}
The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.}
\item {\selectlanguage{english}\color{black}
The Grid/Web Service checks the
{\textless}saml:AuthnStatement{\textgreater} from the session context
to see if the session is still valid through the SecHandler called
{\textquotedblleft}SAML SecHandler{\textquotedblright}. If valid,
service handles the service processing and returns the response to WS
client. Note that service requires that WS client is from the same
connection as the one on which user agent contact SP service, in order
to guarantee that the validity of SSO profile result effects the WS
client/Web Service interaction.}
\end{enumerate}
{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The SP service and other functional service(s) are hosted by the
same container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquoteright}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for the client
side, so that SP and IdP can authenticate themselves to the client. As
required by the SAML2.0 profile, the SP and IdP should have trust
relationship to each other.}

@@

\subsection[\ Short{}-Lived Credential
Service]{\foreignlanguage{english}{\ }Short-Lived Credential Service}
{\selectlanguage{english}\color{black}
\ \ \ \ However, most of the widely used Grid middlewares are based on
GSI while GSI requires mutual authentication. Also for Web Service
based Grid solution, we cannot prevent service side from requiring
client X.509 certificate. Based on the solution described in Section 9,
a short lived credential service (SLCS) is implemented by which user
can get a short-lived X.509 certificate without being bothered to
contact any registration authority (RA) or certificate authority (CA).}

{\selectlanguage{english}\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure
\ref{seq:refFigure6} (from step 1 to step 8), which is the same as in
Figure \ref{seq:refFigure5}, except that step 7 and step 8 are invoked
for the SLCS certificate request and response.}

\begin{center}
\includegraphics[width=3.7689in,height=3.2055in]{SecurityFrameworkofARC1-img8.png}
\end{center}
{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure6}}.Short
lived credential service
\par}

@@

{\selectlanguage{english}\color{black}
\stepcounter{Bibitem}{\theBibitem}.\foreignlanguage{english}{Web Service
Security Username Token Profile 1.1.
}\url{http://www.oasis-open.org/committees/download.php/16782/wss-v1.1-spec-os-UsernameTokenProfile.pdf}}

@@

{\selectlanguage{english}\color{black}
\stepcounter{Bibitem}{\theBibitem}. OASIS Web Services Security (WSS)
TC.
\url{http://www.oasis-open.org/committees/tc_home.php?wg_abbrev=wss}}
\end{document}

>>>>

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5

@@

\documentclass{article}

@@

\usepackage{amsmath,amssymb,amsfonts,textcomp}

@@

\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}

@@

\renewcommand\thesection{\arabic{section}.}
\renewcommand\thesubsection{\arabic{subsection}.}
\renewcommand\thesubsubsection{\arabic{subsection}.\arabic{subsubsection}.}
\renewcommand\theparagraph{\arabic{subsection}.\arabic{subsubsection}.\arabic{paragraph}.}

@@

\newcommand\liststyleLi{%

@@

\setlength\paperwidth{8.2673in}
\setlength\paperheight{11.6925in}

@@

@@

\bigskip
\clearpage\clearpage\setcounter{page}{1}\pagestyle{Convertv}

@@

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{delegtion.pdp} -- Delegation PDP}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The Delegation PDP is basically similar to Arc PDP, except it uses the
delegation policy parsed from remote proxy credential by
\textit{delegation.collector}, and evaluates the request against
delegation policy. See section 6for the design idea and use case of
delegation policy in fine-grained identity delegation.}

@@

{\selectlanguage{english}\itshape\color{black}
 Rule (1-)}

{\selectlanguage{english}\itshape\color{black}
  Subjects (1)}

{\selectlanguage{english}\itshape\color{black}
   Subject (1-)}

{\selectlanguage{english}\itshape\color{black}
    Attribute (1-)}

{\selectlanguage{english}\itshape\color{black}
   Resources (0-1)}

{\selectlanguage{english}\itshape\color{black}
   Resource (1-)}

{\selectlanguage{english}\itshape\color{black}
  Actions (0-1)}

{\selectlanguage{english}\itshape\color{black}
   Action (1-)}

{\selectlanguage{english}\itshape\color{black}
  Conditions (0-1)}

{\selectlanguage{english}\itshape\color{black}
   Condition (1-)}

{\selectlanguage{english}\itshape\color{black}
    Attribute (1-)}

@@

{\selectlanguage{english}\itshape\color{black}
 RequestItem (1-)}

{\selectlanguage{english}\itshape\color{black}
  Subject (1-)}

{\selectlanguage{english}\itshape\color{black}
   SubjectAttribute (1-)}

{\selectlanguage{english}\itshape\color{black}
  Resource (0-)}

{\selectlanguage{english}\itshape\color{black}
  Action (0-)}

{\selectlanguage{english}\itshape\color{black}
  Context (0-)}

{\selectlanguage{english}\itshape\color{black}
   ContextAttribute (1-)}

@@

{\selectlanguage{english}\upshape\color{black}
Each kind of Security Attribute is represented by own class inherited
from parent SecAttr class
{\textless}arc/message/SecAttr.h{\textgreater}. Each Security Attribute
stores it{\textquotesingle}s information in internal format and is
capable to export it to one of predefined formats using Export()
method. Currently only supported format is ARC Policy/Request XML
document described in Section 7.1and 7.2}

{\selectlanguage{english}\upshape\color{black}
Collectors of Security Attributes instantiate corresponding classes and
link them to Secuirity Attributes containers - MessageAuth
{\textless}arc/message/MessageAuth.h{\textgreater} and
MessageAuthContext {\textless}arc/message/Message.h{\textgreater}
storing collected attributes per request and per session
correspondingly. Each attribute is assigned a name. Current
implementations of Security Attributes Collectors are either integrated
into existing MCCs or implemented as separate SecHandler plugins. See
Section 5.2for available Collectors and corresponding Security
Attributes. }

@@

\liststyleWWviiiNumviii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Arc PDP makes use of Security Attributes containing identities of
client, resource and requested action. It evaluates either all or
selected set of attributes against specified Policy documents thus
making it possible to enforce policies defined/selected by service
providers. }
\item {\selectlanguage{english}\color{black}
Delegation PDP is described below in Section 6.3}
\end{itemize}
\subsubsection[Available collectors]{Available collectors}
\label{bkm:Ref204009636}{\selectlanguage{english}\upshape\color{black}
Here Security Attribute collectors distributed as part of the ARC1 are
described except those used for Delegation Restrictions. Those are
described in Section 6.2}

@@

{\selectlanguage{english}\color{black}
Each set of attributes is accompanied by identifier of service which
provided those attributes. It is made of \textit{voname} element with
name of VO followed by optional element \textit{hostname} with hostname
and port of service. Here is an example}

@@

{\selectlanguage{english}\color{black}
Which is needed to describe is the configuration of trusted certificates
to constrain the Attribute Certificate (AC) which the service would
accept. The trusted certificates should be organized in a chunk which
contains a suit of DN of trusted certificate in a chain
(\textit{{\textless}VOMSCertTrustDNChain{\textgreater}}), in which the
first line is the DN of the VOMS server certificate (cert0) which is
used to sign the Attribute Certificate (AC), the second line is the DN
of the corresponding issuer certificate(cert1) which is used to sign
cert0. So if there are one or more intermediate issuers, then there
should be 3 or more than 3 lines of DN in this chunk (considering cert0
and the root CA certificate, plus the intermediate certificate).
Regular expression is supported as well for match-making, in this case,
only one line of regular expression is needed under one chain. Also,
the trusted certificate chain can also be acquired from an independent
text file including the same format of content.}

{\selectlanguage{english}\color{black}
The chain (\textit{{\textless}VOMSCertTrustDNChain{\textgreater}})
should be configured under the configuration of TLS MCC. There also
could be a few chains, if there are a few VOMS servers which are
trusted by this service container.}

\begin{center}
\tablehead{}\begin{supertabular}{|m{5.6886597in}|}
\hline
{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDN{\textgreater}/O=Grid/O=NorduGrid/CN=host/arthur.hep.lu.se{\textless}/tls:VOMSCertTrustDN{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDN{\textgreater}/O=Grid/O=NorduGrid/CN=NorduGrid
Certification Authority{\textless}/tls:VOMSCertTrustDN{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDN{\textgreater}/DC=ch/DC=cern/OU=computers/CN=voms.cern.ch{\textless}/tls:VOMSCertTrustDN{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDN{\textgreater}/DC=ch/DC=cern/CN=CERN
Trusted Certification
Authority{\textless}/tls:VOMSCertTrustDN{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustRegex{\textgreater}\^{}/O=Grid/O=NorduGrid{\textless}/tls:VOMSCertTrustRegex{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/tls:VOMSCertTrustDNChain{\textgreater}}

\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDNChainsLocation{\textgreater}./{\textless}/tls:VOMSCertTrustDNChainsLocation{\textgreater}\\\hline
\end{supertabular}
\end{center}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at SOAP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/endpoint &
\selectlanguage{english}\color{black} To element of WS-Addressing
structure\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/operation &
\selectlanguage{english}\color{black} SOAP top level element name
without namespace prefix\\\hline
\selectlanguage{english}\color{black} Context &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace &
\selectlanguage{english}\color{black} Namespace of SOAP top level
element\\\hline
\end{supertabular}
\end{flushleft}
\subsection[Delegation]{Delegation}
\label{bkm:Ref204009393}\subsubsection[Delegation
Architecture]{Delegation Architecture}
\label{bkm:Ref204009914}{\selectlanguage{english}\upshape\color{black}
In current implementation delegation is achieved through Identity
Delegation implemented using X509 Proxy Certificates as defined in RFC
3820. Client wishing to allow service to act on it{\textquotesingle}s
behalf provides Proxy Certificate to the service using Web Service
based Delegation interface described in Section 6.4}

@@

{\selectlanguage{english}\upshape\color{black}
Each deployment implementing Delegation Restrictions must use dedicated
Security Handler plugin (see section 5.1) to collect all Policy
documents from Proxy Certificates used for establishing secure
connection. Then those documents must be processed by dedicated Policy
Decision Point plugin (see section 2.3) to make a final decision based
on collected Policies and various information about
client{\textquotesingle}s identity and requested operation. Service or
MCC chain supporting Delegation Restrictions must accept negative
decision of this PDP as final and do not override it with any other
decision based on other policies.}

\subsubsection[Delegation Collector]{Delegation Collector}
\label{bkm:Ref204009734}{\selectlanguage{english}\upshape\color{black}
This Security Attribute is collected by dedicated Security Handler
plugin named {\textquotedbl}delegation.collector{\textquotedbl}
avaialble as part of the ARC1 distribution. It extracts policy document
stored inside X509 certificate proxy extension as defined in RFC3820
and described in Section 6.1All proxy certificates in a chain provided
by client are examined and all available policies are extracted. }

@@

\subsubsection[Delegation interface]{Delegation interface}
\label{bkm:Ref204009766}{\selectlanguage{english}\upshape\color{black}
Delegation interface in the ARC1 is implemented using Web Service
approach. Each ARC1 service wishing to act on behalf of client identity
implements this interface in order to accept delegated credentials.
Here is how delegation procedure works (also shown in figures
\ref{seq:refFigure5} and \ref{seq:refFigure6}) :}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure5}}. The
flow diagram of delegation procedure with multiple second step and
session expiration. 
\par}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure6}}. The
flow diagram of delegation procedure with certificate transfered as
payload of service specific message. 
\par}

@@

{\selectlanguage{english}\upshape\color{black}
See Section 7.7for the explanation of ARC Policy.}

@@

{\selectlanguage{english}\upshape\color{black}
There is an example policy for echo service below. See Section 7.1for
the policy schema. The example policy is \ made of following elements:
}

@@

\subsubsection[PDP Service Invoker configuration]{PDP Service Invoker
configuration}

@@

\subsubsection[X509Token SecHandler configuration]{X509Token SecHandler
configuration}
{\selectlanguage{english}\upshape\color{black}
Configuration XML schema with comments available at
\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}{\textstyleInternetlink{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/x509tokensh/X509TokenSH.xs}}\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}{\textstyleInternetlink{d}}.}

@@

\subsection[Using Shibboleth IdP for Authentication and Attribute-based
Authorization]{Using \foreignlanguage{english}{Shibboleth} IdP for
Authentication and Attribute-based Authorization}
{\selectlanguage{english}\color{black}
\ \ \ \ In grid community, GSI (grid security infrastructure) is the
de-facto standard about transport level communication for the legacy
grid solution, which implements some enhancement (such as delegation)
based on standard SSL3.0/TLS1.0. In ARC1, besides that GSI is supported
for talking with external grid services which are based on GSI, the
standard TLS/SSL is also supported.}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure
{\refstepcounter{Figure}\theFigure\label{seq:refFigure7}}.\textbf{
}SAML2.0 SSO profile in ARC
\par}

{\selectlanguage{english}\color{black}
\ The steps shows in Figure \ref{seq:refFigure7} are described as
follows:}

\liststyleLi
\begin{enumerate}
\item {\selectlanguage{english}\color{black}
The client uses the user agent interface to launch a HTTP request
including the IdP name (to which the user belongs) to the service side.
The endpoint of the SP (Service Provider) service is the same as that
of the other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that the user who would
access the target services should better know where is he from
initially.}
\item {\selectlanguage{english}\color{black}
The SP Service searches the metadata (we use the same metadata format as
defined in Shibboleth) and gets the location of the single sign-on
service (hosted in IdP) and also the location of assertion consuming
service (hosted in this SP itself) in order to compose the SAML
{\textless}samlp:AuthnRequest{\textgreater} message. Then SP Service
issues this {\textless}samlp:AuthnRequest{\textgreater} message by
using its own X.509 certificate (note that in the SAML SSO profile,
X.509 certificates are still needed for IdP and SP) and sends back to
user agent.}
\item {\selectlanguage{english}\color{black}
User agent sends the {\textless}samlp:AuthnRequest{\textgreater} message
to the Identity Provider.}
\item {\selectlanguage{english}\color{black}
Identity Provider requires an act of authentication. The authentication
mechanism is outside of the SAML2.0 SSO profile. Shibboleth IdP
implementation chooses some login handlers for authentication. The
current user agent implementation is compatible with the
Username/Password login handler of Shibboleth IdP. Through the HTTP
protocol, the user agent will feed IdP with the username/password which
has been given by the caller of user agent interface.}
\item {\selectlanguage{english}\color{black}
Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquoteright}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider.}
\item {\selectlanguage{english}\color{black}
The SP Service verifies and checks the SAML response, decrypts and
stores the SAML assertion into session/connection context. The SAML
assertion includes the {\textless}saml:AuthnStatement{\textgreater} and
{\textless}saml:AttributeStatement{\textgreater}.}
\item {\selectlanguage{english}\color{black}
The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.}
\item {\selectlanguage{english}\color{black}
The Grid/Web Service checks the
{\textless}saml:AuthnStatement{\textgreater} from the session context
to see if the session is still valid through the SecHandler called
{\textquotedblleft}SAML SecHandler{\textquotedblright}. If valid,
service handles the service processing and returns the response to WS
client. Note that service requires that WS client is from the same
connection as the one on which user agent contact SP service, in order
to guarantee that the validity of SSO profile result effects the WS
client/Web Service interaction.}
\end{enumerate}
{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The SP service and other functional service(s) are hosted by the
same container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquoteright}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for the client
side, so that SP and IdP can authenticate themselves to the client. As
required by the SAML2.0 profile, the SP and IdP should have trust
relationship to each other.}

@@

\subsection[\ Short-Lived Credential
Service]{\foreignlanguage{english}{\ }Short-Lived Credential Service}
{\selectlanguage{english}\color{black}
\ \ \ \ However, most of the widely used Grid middlewares are based on
GSI while GSI requires mutual authentication. Also for Web Service
based Grid solution, we cannot prevent service side from requiring
client X.509 certificate. Based on the solution described in Section 9,
a short lived credential service (SLCS) is implemented by which user
can get a short-lived X.509 certificate without being bothered to
contact any registration authority (RA) or certificate authority (CA).}

{\selectlanguage{english}\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure
\ref{seq:refFigure8} (from step 1 to step 8), which is the same as in
Figure \ref{seq:refFigure7}, except that step 7 and step 8 are invoked
for the SLCS certificate request and response.}

\begin{center}
\includegraphics[width=3.7689in,height=3.2055in]{SecurityFrameworkofARC1-img8.png}
\end{center}
{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure8}}.Short
lived credential service
\par}

@@

{\selectlanguage{english}\color{black}
\textstyleInternetlink{\textcolor{black}{\stepcounter{Bibitem}{\theBibitem}}}\textstyleInternetlink{\textcolor{black}{.}}\textstyleInternetlink{\foreignlanguage{english}{\textcolor{black}{Web
Service Security Username Token Profile 1.1.
}}}\url{http://www.oasis-open.org/committees/download.php/16782/wss-v1.1-spec-os-UsernameTokenProfile.pdf}}

@@

{\selectlanguage{english}\color{black}
\textstyleInternetlink{\textcolor{black}{\stepcounter{Bibitem}{\theBibitem}}}\textstyleInternetlink{\textcolor{black}{.
OASIS Web Services Security (WSS) TC.
}}\url{http://www.oasis-open.org/committees/tc_home.php?wg_abbrev=wss}}
\end{document}
